---
title: "Homework5"
author: "Lia"
date: "2023-11-26"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    number_sections: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bootstrapping Standard Erros and CIs for Linear Models. 
Load the packages first. 
```{r}
library(curl)
library(dplyr)
library(boot)
```
## Challenge 1
**Description: **Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).


Read the file. 
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
KC <- read.csv(f, header=TRUE, sep=",", stringsAsFactors=FALSE) %>% filter(!is.na(HomeRange_km2)) %>% filter(!is.na(Body_mass_female_mean))
```

Modeling. 
```{r}
lHR <- log(KC$HomeRange_km2)
lBmfm <- log(KC$Body_mass_female_mean)
limod <- lm(lHR ~ lBmfm, data=KC)
summary(limod)
coeffs <- limod$coefficients
coeffs
```

## Challenge 2
**Description: **Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.

```{r}
set.seed(123)
fun <- function(formula, data, indices) {
  d <- data[indices, ]
  fit <- lm(formula, data=d)
  return(coef(fit))
}
reps <- boot(data=KC, statistic=fun, R=1000, formula=log(HomeRange_km2) ~ log(Body_mass_female_mean))
reps
plot(reps)
```

```{r}
confint(limod, level=0.95)
boot.ci(reps, type="bca", index=1) #intercept of model
boot.ci(reps, type="bca", index=2) #disp predictor variable
```

boot.ci() with type="bca" generates the adjusted bootstrap percentile (BCa) interval. reps here is an object containing the output of a bootstrap calculation so it will not cuase repeating bootstrapping. 

**Question 1: **
How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

**Answer: **
SDE of bootstrapping β coefficients are 0.58297075 and 0.07553405. It looks better than  0.67293 and 0.08488 which comes from the model. 

**Question 2: **
How does the latter compare to the 95% CI estimated from your entire dataset?

**Answer: **
In the bootstrapped method, intercept is -10.766 and -8.372, with slope of 0.898 and 1.212. In the non-bootstrapped method, intercept is -10.7720889 and -8.110374, with slope of 0.8685707 and 1.204292. the intercept in the bootstrapped method looks tighter. 